Priors

### 2023-07-19 analysis/priors.Rmd
prior illustrations

lambda_pl <- ggplot(mapping = aes(x = x, y = y)) +
  geom_line(data = lambda_dat, direction = "vh") +
  geom_segment(data = prev_est_vir, mapping = aes(xend = x, yend = 0, color = study), linetype = "dotted") +
  geom_segment(data = prev_est_vir, mapping = aes(yend = y, xend = 0, color = study), linetype = "dotted") +
  geom_point(data = prev_est_vir, mapping = aes(color = study), shape = 17, size = 2) +
  geom_text(data = prev_est_vir %>% dplyr::filter(study != "Lever (2000)"), mapping = aes(label = study, color = study), size = 8 / cm(1), nudge_x = log(1.35), nudge_y = .02) +
  geom_text(data = prev_est_vir %>% dplyr::filter(study == "Lever (2000)"), mapping = aes(label = study, color = study), size = 8 / cm(1), nudge_y = 0.05) +
  scale_x_continuous(expand = expansion(mult = c(0,.025)), breaks = c(0, 0.5, 1, 2, 5, 10), trans = scales::pseudo_log_trans(base = 10)) +
  scale_y_continuous(expand = expansion(mult = c(0,.025)), labels = scales::percent_format(suffix = "")) +
  scale_color_manual(values = wes_palette("Cavalcanti1")) +
  labs(x = "Viral inactivation rate (quanta/h)", y = "Cumulative probability (%)") +
  theme_custom() +
  theme(legend.position = "none")

>>>>

lambda_pl <- ggplot(mapping = aes(x = x, y = y)) +
  geom_line(data = lambda_dat, direction = "vh") +
  geom_segment(data = prev_est_vir, mapping = aes(xend = x, yend = 0, color = study), linetype = "dotted") +
  geom_segment(data = prev_est_vir, mapping = aes(yend = y, xend = 0, color = study), linetype = "dotted") +
  geom_point(data = prev_est_vir, mapping = aes(color = study), shape = 17, size = 2) +
  geom_text(data = prev_est_vir %>% dplyr::filter(study != "Lever (2000)"), mapping = aes(label = study, color = study), size = 8 / cm(1), nudge_x = log(1.13), nudge_y = .02) +
  geom_text(data = prev_est_vir %>% dplyr::filter(study == "Lever (2000)"), mapping = aes(label = study, color = study), size = 8 / cm(1), nudge_y = 0.05) +
  scale_x_continuous(expand = expansion(mult = c(0,.025)), breaks = c(0, 0.5, 1, 2, 5, 10), trans = scales::pseudo_log_trans(base = 10)) +
  scale_y_continuous(expand = expansion(mult = c(0,.025)), labels = scales::percent_format(suffix = "")) +
  scale_color_manual(values = wes_palette("Cavalcanti1")) +
  labs(x = "Viral inactivation rate (quanta/h)", y = "Cumulative probability (%)") +
  theme_custom() +
  theme(legend.position = "none")
